Analysis of Physical Activity Survey(2022)

### 2023-05-04 docs/index.Rmd
setup

---
title: "Analysis of Physical Activity Survey(2022)"
author: "Jonathan Goodwin"
date: "2022 March 7"
output:
  html_document: default
  bookdown: default
  pdf_document: default
header-includes:
- \usepackage{float}
- \floatplacement{figure}{H}
abstract: Recreational activity and physical fitness are important factors in determining
  the health and safety of a society. We obtain data regarding the activity of individuals
  of different states and age groups as well as their respective distance to a park.
  We find that citizens who live closer to parks are more likely to be physically
  active, and that younger citizens are more likely to be physically active then older
  ones. These findings have implications for the future development of public recreational
  structures.
toc: no
bibliography: references.bib
---
```{r setup, include=FALSE,warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message= FALSE, fig.pos = 'H')
library(tidyverse)
library(kableExtra)
library(reshape2)
library(here)
```
```{r, echo = F}
### Reading CSV and setting seed###
set.seed(1)
Data <- 
  read.csv(here::here("outputs/data/cleaned_physical_activity.csv"))
Data1 <- read.csv(here::here("outputs/data/cleaned_walk_or_bike.csv"))
```

>>>>

---
title: "Analysis of Physical Activity Survey(2022)"
author: "Jonathan Goodwin"
date: "2022 March 7"
output:
  html_document:
    keep_md: TRUE
  bookdown: default
  pdf_document: default
header-includes:
- \usepackage{float}
- \floatplacement{figure}{H}
abstract: Recreational activity and physical fitness are important factors in determining
  the health and safety of a society. We obtain data regarding the activity of individuals
  of different states and age groups as well as their respective distance to a park.
  We find that citizens who live closer to parks are more likely to be physically
  active, and that younger citizens are more likely to be physically active then older
  ones. These findings have implications for the future development of public recreational
  structures.
toc: no
bibliography: references.bib
---
```{r setup, include=FALSE,warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message= FALSE, fig.pos = 'H')
library(tidyverse)
library(kableExtra)
library(reshape2)
library(here)
```
```{r, echo = F}
### Reading CSV and setting seed###
set.seed(1)
Data <- 
  read.csv(here::here("outputs/data/cleaned_physical_activity.csv"))
Data1 <- read.csv(here::here("outputs/data/cleaned_walk_or_bike.csv"))
```
